---
title: "LeetCode_Analysis"
author: "Karen D. Wang"
date: "2024-08-11"
output: html_document
---

```{r}
library(tidyverse)
library(lme4)
library(lubridate)
```

```{r set-theme, echo=FALSE}
theme_set(
  theme_classic() + #set the theme 
    theme(text = element_text(family = "Times", size = 18)) #set the default text size
)
```

# Import Data
```{r}
# setwd("/path/to/parent/folder")

#Get list of all CSV files in the 'csv_file' folder
csv_files <- list.files(path = "csv_file", pattern = "*.csv", full.names = TRUE)
filtered_files <- list.files(path = "filtered_csv_file", pattern = "*.csv", full.names = TRUE)

#Read all CSV files into a list of dataframes
data_frames <- lapply(csv_files, read.csv)
filtered_data_frames <- lapply(filtered_files, read.csv)

#Name the dataframes based on the file names
names(data_frames) <- tools::file_path_sans_ext(basename(csv_files))
names(filtered_data_frames) <- tools::file_path_sans_ext(basename(filtered_files))

#Create individual dataframes in the global environment
#list2env(data_frames, envir = .GlobalEnv)
```

# Process the 'time_delta" variable
```{r}
# Function to convert time_delta to seconds
convert_to_seconds <- function(time_string) {
  # Split the string into days and time
  parts <- strsplit(time_string, " days ")[[1]]
  
  days <- as.numeric(parts[1])
  
  # If there's a time part, parse it; otherwise, use 0
  if (length(parts) > 1) {
    time <- lubridate::hms(parts[2])
  } else {
    time <- lubridate::hms("00:00:00")
  }
  
  # Convert to seconds
  total_seconds <- days * 24 * 60 * 60 + as.numeric(time)
  
  return(total_seconds)
}

# create a new variable that shows time delta in seconds
# Apply the conversion to each dataframe
for (i in seq_along(data_frames)) {
  if ("time_delta" %in% names(data_frames[[i]])) {
    data_frames[[i]]$time_delta_seconds <- sapply(data_frames[[i]]$time_delta, convert_to_seconds)
  } else {
    warning(paste("time_delta column not found in", names(data_frames)[i]))
  }
}

for (i in seq_along(filtered_data_frames)) {
  if ("time_delta" %in% names(filtered_data_frames[[i]])) {
    filtered_data_frames[[i]]$time_delta_seconds <- sapply(filtered_data_frames[[i]]$time_delta, convert_to_seconds)
  } else {
    warning(paste("time_delta column not found in", names(filtered_data_frames)[i]))
  }
}

# for (df_name in names(data_frames)) {
#   if ("time_delta" %in% names(get(df_name))) {
#     assign(df_name, within(get(df_name), {
#       time_delta_seconds <- sapply(time_delta, convert_to_seconds)
#     }))
#   } else {
#     warning(paste("time_delta column not found in", df_name))
#   }
# }
```

# Density plot of all time_delta
```{r}
# Combine all 'time_delta_seconds' data into one dataframe
all_time_delta_seconds <- do.call(rbind, lapply(data_frames, function(df) {
  data.frame(
    time_delta_seconds = df$time_delta_seconds,
    source = rep(deparse(substitute(df)), nrow(df))
  )
}))
```

```{r - descriptive statistics}
# Convert time_delta_seconds to minutes and calculate statistics
time_delta_stats <- all_time_delta_seconds %>%
  mutate(time_delta_minutes = time_delta_seconds / 60) %>%
  summarise(
    mean_minutes = mean(time_delta_minutes, na.rm = TRUE),
    median_minutes = median(time_delta_minutes, na.rm = TRUE),
    min_minutes = min(time_delta_minutes, na.rm = TRUE),
    max_minutes = max(time_delta_minutes, na.rm = TRUE),
    percentile_95 = quantile(time_delta_minutes, 0.95, na.rm = TRUE)
  )

# Print the results
cat("Time Delta Statistics (in minutes):\n")
cat("Mean:", round(time_delta_stats$mean_minutes, 2), "\n")
cat("Median:", round(time_delta_stats$median_minutes, 2), "\n")
cat("Minimum:", round(time_delta_stats$min_minutes, 2), "\n")
cat("Maximum:", round(time_delta_stats$max_minutes, 2), "\n")
cat("95th Percentile:", round(time_delta_stats$percentile_95, 2), "\n")
```
```{r - percentage over hours}
percentage_over_hour <- nrow(all_time_delta_seconds %>% filter(time_delta_seconds > 60*60)) / 
                        nrow(all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than one hour:", round(percentage_over_hour, 2), "%\n")

percentage_over_two_hour <- nrow(all_time_delta_seconds %>% filter(time_delta_seconds > 2*60*60)) / 
                        nrow(all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than two hours:", round(percentage_over_two_hour, 2), "%\n")

percentage_over_three_hour <- nrow(all_time_delta_seconds %>% filter(time_delta_seconds > 3*60*60)) / 
                        nrow(all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than three hours:", round(percentage_over_three_hour, 2), "%\n")
```

```{r - density plot}
# Create corrected density plot of log(time_delta)
ggplot(all_time_delta_seconds, aes(x = time_delta_seconds/60)) +
  geom_density(fill = "skyblue", color = "darkblue", alpha = 0.7) +
  scale_x_log10(
    breaks = c(0.1, 1, 10, 100, 1000, 10000),
    labels = c("0.1", "1", "10", "100", "1000", "10000"),
    name = "Minutes (log scale)"
  ) +
  labs(title = "Density Plot of log(time_delta)",
       y = "Density") +
  theme_minimal() +
  geom_vline(aes(xintercept = 1.5), color = "red", linetype = "dashed") +
  geom_vline(aes(xintercept = 493.1), color = "blue", linetype = "dashed") +
  annotate("text", x = 1.5, y = Inf, label = "Median (1.5 mins)", color = "red", vjust = 2, hjust = -0.1) +
  annotate("text", x = 493.1, y = Inf, label = "Mean (493.1 mins)", color = "blue", vjust = 2, hjust = 1.1)

ggsave("log_time_delta_density_plot.png", width = 10, height = 6)
```
The data is highly skewed to the right with a long tail of larger values.

# Check the numbe of actions
```{r - all action count}
for (name in names(data_frames)) {
  cat("Dataframe:", name, "\n")
  print(table(data_frames[[name]]$action))
  cat("\n")
}
```

# Filter to include only "Started" and "Submit" action types
```{r}
# Combine all 'time_delta_seconds' data into one dataframe
filtered_all_time_delta_seconds <- do.call(rbind, lapply(filtered_data_frames, function(df) {
  data.frame(
    time_delta_seconds = df$time_delta_seconds,
    source = rep(deparse(substitute(df)), nrow(df))
  )
}))
```

```{r - descriptive statistics}
# Convert time_delta_seconds to minutes and calculate statistics
time_delta_stats <- filtered_all_time_delta_seconds %>%
  mutate(time_delta_minutes = time_delta_seconds / 60) %>%
  summarise(
    mean_minutes = mean(time_delta_minutes, na.rm = TRUE),
    median_minutes = median(time_delta_minutes, na.rm = TRUE),
    min_minutes = min(time_delta_minutes, na.rm = TRUE),
    max_minutes = max(time_delta_minutes, na.rm = TRUE),
    percentile_95 = quantile(time_delta_minutes, 0.95, na.rm = TRUE)
  )

# Print the results
cat("Time Delta Statistics (in minutes):\n")
cat("Mean:", round(time_delta_stats$mean_minutes, 2), "\n")
cat("Median:", round(time_delta_stats$median_minutes, 2), "\n")
cat("Minimum:", round(time_delta_stats$min_minutes, 2), "\n")
cat("Maximum:", round(time_delta_stats$max_minutes, 2), "\n")
cat("95th Percentile:", round(time_delta_stats$percentile_95, 2), "\n")
```
```{r - percentage over hours}
percentage_over_hour <- nrow(filtered_all_time_delta_seconds %>% filter(time_delta_seconds > 60*60)) / 
                        nrow(filtered_all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than one hour:", round(percentage_over_hour, 2), "%\n")

percentage_over_two_hour <- nrow(filtered_all_time_delta_seconds %>% filter(time_delta_seconds > 2*60*60)) / 
                        nrow(filtered_all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than two hours:", round(percentage_over_two_hour, 2), "%\n")

percentage_over_three_hour <- nrow(filtered_all_time_delta_seconds %>% filter(time_delta_seconds > 3*60*60)) / 
                        nrow(filtered_all_time_delta_seconds %>% filter(!is.na(time_delta_seconds))) * 100
cat("Percentage of time_delta longer than three hours:", round(percentage_over_three_hour, 2), "%\n")
```

```{r - density plot}
# Create corrected density plot of log(time_delta)
ggplot(filtered_all_time_delta_seconds, aes(x = time_delta_seconds/60)) +
  geom_density(fill = "skyblue", color = "darkblue", alpha = 0.7) +
  scale_x_log10(
    breaks = c(0.1, 1, 10, 100, 1000, 10000),
    labels = c("0.1", "1", "10", "100", "1000", "10000"),
    name = "Minutes (log scale)"
  ) +
  labs(title = "Density Plot of log(time_delta)",
       y = "Density") +
  theme_minimal() +
  geom_vline(aes(xintercept = 4.02), color = "red", linetype = "dashed") +
  geom_vline(aes(xintercept = 854.98), color = "blue", linetype = "dashed") +
  annotate("text", x = 4.02, y = Inf, label = "Median (4 mins)", color = "red", vjust = 2, hjust = -0.1) +
  annotate("text", x = 854.98, y = Inf, label = "Mean (855 mins)", color = "blue", vjust = 2, hjust = 1.1)

ggsave("log_time_delta_density_plot.png", width = 10, height = 6)
```
```{r - started and submit action count}
for (name in names(filtered_data_frames)) {
  cat("Dataframe:", name, "\n")
  print(table(filtered_data_frames[[name]]$action))
  cat("\n")
}
```

#RQ1 Is there a correlation between the number of submits and the time interval between submits?
#RQ2 Is there a correlation between the number of submits and final score
```{r warning=FAlSE, message=FALSE}

# Function to analyze a single dataframe
analyze_dataframe <- function(df) {
  result <- df %>%
    group_by(id) %>%
    summarise(
      median_time_delta_seconds = median(time_delta_seconds, na.rm = TRUE),
      total_submits = sum(action == "Submit", na.rm = TRUE),
      final_score = last(marks[action == "Submit"], default = NA)
    ) %>%
    ungroup()
  

}


create_scatterplot <- function(df, x_var, y_var, color_var = NULL, title) {
  p <- ggplot(df, aes(x = !!sym(x_var), y = !!sym(y_var))) +
    geom_point(alpha = 0.6) +
    geom_smooth(method = "lm", se = FALSE, color = "red", linetype = "dashed") +
    labs(
      title = title,
      x = gsub("_", " ", str_to_title(x_var)),
      y = gsub("_", " ", str_to_title(y_var))
    ) +
    theme_minimal()
  
  if (!is.null(color_var)) {
    p <- p + aes(color = !!sym(color_var)) +
      scale_color_viridis_c() +
      labs(color = gsub("_", " ", str_to_title(color_var)))
  }
  
  if (y_var == "median_time_delta_seconds") {
    p <- p + scale_y_log10()
  }
  
  return(p)
}

# Apply the analysis function to all dataframes and create plots
for (name in names(filtered_data_frames)) {
  df <- filtered_data_frames[[name]]
  result <- analyze_dataframe(df)
  
  # Create and save the first type of scatterplot (submits vs pause duration, colored by final score)
  plot1 <- create_scatterplot(result, 
                              x_var = "total_submits", 
                              y_var = "median_time_delta_seconds", 
                              color_var = "final_score", 
                              title = paste("Submits vs Pause Duration for", name))
  print(plot1)
  ggsave(paste0("scatterplot_submits_pause_", name, ".png"), plot1, width = 10, height = 6)
  
  # Create and save the second type of scatterplot (submits vs final score)
  plot2 <- create_scatterplot(result, 
                              x_var = "total_submits", 
                              y_var = "final_score", 
                              title = paste("Submits vs Final Score for", name))
  print(plot2)
  ggsave(paste0("scatterplot_submits_score_", name, ".png"), plot2, width = 10, height = 6)
  
  
}
```

```{r}
analyze_dataframe <- function(df) {
  df %>%
    group_by(id) %>%
    summarise(
      total_submits = sum(action == "Submit", na.rm = TRUE),
      final_score = last(marks[action == "Submit"], default = NA)
    ) %>%
    ungroup()
}

# Function to get top submitters
get_top_submitters <- function(df, n = 3) {
  df %>%
    arrange(desc(total_submits)) %>%
    slice_head(n = n) %>%
    select(id, total_submits, final_score)
}

# Initialize an empty dataframe to store all top submitters
all_top_submitters <- data.frame()

# Main analysis loop for top submitters
for (name in names(filtered_data_frames)) {
  df <- filtered_data_frames[[name]]
  result <- analyze_dataframe(df)
  
  top_submitters <- get_top_submitters(result)
  
  # Add a column to indicate which dataframe this is from
  top_submitters$dataframe <- name
  
  # Append to the all_top_submitters dataframe
  all_top_submitters <- bind_rows(all_top_submitters, top_submitters)
  print(top_submitters)
}

# Analyze for repeated IDs
repeated_ids <- all_top_submitters %>%
  group_by(id) %>%
  summarise(
    frequency = n(),
    dataframes = paste(dataframe, collapse = ", "),
    total_submits = paste(total_submits, collapse = ", "),
    final_scores = paste(final_score, collapse = ", ")
  ) %>%
  filter(frequency > 1) %>%
  arrange(desc(frequency))

# Print the results
cat("IDs appearing in top submitters more than once:\n")
print(repeated_ids)
```


